\cvletter{}

\cvparagraph{}
  {My name is Mathias Wiesbauer, and I’m writing to apply for a Software Development Engineer (ID 901717) position at Amazon AWS.}
\cvparagraph{}
  {I've always had a particular interest in networking and in the underlying technologies that enable the internet as we know it. Having worked as a systems engineer, I've used the "it's always DNS" line more than once. But this answer did not satisfy for long; therefore, I decided to dive deep and completed my CCNA, MCSA and graduate networking class. In the latter writing a DNS client and implementing the DNS protocol to query DNS servers.}
\cvparagraph{}
  {Learning never stops, and I would like to focus my further learning on distributed systems as part of being enrolled in a CS Masters program. And where better to take my curiosity than to a company that coined the term cloud computing and a product that is committed to 100\% Availability. I would be thrilled to join the team and being able to contribute to the success of Route 53.}
\cvparagraph{}
  {What can I offer Amazon AWS? Experience in programming languages such as Python and Java. Over the past five years, I've designed and built a cloud-based software product in close collaboration with customers because I saw an opportunity and took ownership. I've earned and retained customers trust by always going the extra mile. The Amazon leadership principles do not ring hollow to me but are a driving force that empowers employees.}
\cvparagraph{}
  {Please find my resume attached. Should you have any questions about my materials or application, please don’t hesitate to contact me.}
\cvparagraph{}
  {Thank you for your consideration, and I am excited to meet you and discuss how I can contribute to Route 53.}